%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, letterpaper]{article}
\usepackage[dvipsnames,usenames]{xcolor}
\usepackage{fontspec} 

%%% Hanging indents: args length, number of lines.
%%% \begin{hangparas}{1em}{1}
\usepackage{hanging} 
\usepackage{datetime}
\renewcommand{\dateseparator}{-}
\newdateformat{isodate}{%
\THEYEAR\dateseparator\twodigit{\THEMONTH}\dateseparator\twodigit{\THEDAY}}


% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{letterpaper, textwidth=6in, textheight=9in, marginparsep=1em}



% FONTS
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
\setmainfont [Ligatures={Common},Numbers=OldStyle, BoldFont={* Bold}, ItalicFont={* Italic}]{Minion Pro}
\setsansfont {Neutraface Text}
\setmonofont{Monaco} 
% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Fontin}\&}}
\newcommand{\urltilde}{$\sim$}

% ---- MARGIN YEARS
\setlength{\marginparwidth}{.35in}
\newcommand{\years}[1]{\marginpar{\scriptsize #1}}

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\sffamily\bfseries\upshape\Large}
\subsectionfont{\sffamily\bfseries\upshape\normalsize} 
\subsubsectionfont{\sffamily\mdseries\upshape\normalsize} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[bookmarks, colorlinks, breaklinks]{hyperref}  
\hypersetup{linkcolor=NavyBlue,citecolor=NavyBlue,filecolor=NavyBlue,urlcolor=NavyBlue,pdftitle=Jonathan Keane - CV,pdfauthor=Jonathan Keane,bookmarksopen=true} 

% DOCUMENT
\begin{document}
%\pagestyle{empty}
\thispagestyle{empty} % No page number first page
\reversemarginpar
\raggedright

\begin{table}[!t]
  \begin{tabular*}{6.5in}{r|l}
    \hspace{3in}\textbf{\LARGE\sffamily Jonathan Keane}  &\\
Department of Linguistics & \\
  The University of Chicago & \href{mailto:jonkeane@uchicago.edu}{\textsc{jonkeane@uchicago.edu}}\\
1010 \textsc{e} 59th Street & \href{http://jonkeane.com}{\textsc{jonkeane.com}}\\
    Chicago \textsc{il} 60637 & 312 391 9163 \\
  \end{tabular*}
\end{table}
%%% Begin with soft hyphen “\-” to line up the years marginpar.
\setlength\parindent{0in}
\setlength\parskip{0ex}
\pdfbookmark[0]{Current position}{Current position}
\section*{Current position}
\emph{PhD Student}, University of Chicago, Department of Linguistics\\

\pdfbookmark[0]{Areas of specialization}{Areas of specialization}
\section*{Areas of specialization}
Articulatory phonetics and phonology, computational approaches to linguistics, signed languages, \textsc{asl}, fingerspelling, syntax, morphology

% \section*{Appointments held}
% \noindent
% \years{}

\pdfbookmark[0]{Education}{education}
\section*{Education}
\-\years{2013}PhD (anticipated) in Linguistics, University of Chicago \\
\hspace{2em} \textit{Dissertation title (working)} Towards an articulatory model of handshape:\\
\hspace{4em}What fingerspelling tells us about the phonetics and phonology of handshape in \textsc{asl}.\\
\hspace{2em} \textit{Advisors} Diane Brentari and Jason Riggle

%\-\years{2011}\textsc{MA} (anticipated) in Linguistics, University of Chicago

\-\years{2007}\textsc{BA} (Magna cum Laude) in Linguistics, University of Florida\\
\hspace{2em}\textit{\textsc{BA} Thesis} Nominal Incorporation in English \\
\hspace{2em}\textit{Advisor} D. Gary Miller

\pdfbookmark[0]{Honors + awards}{Honors + awards}
\section*{Honors + awards}
\-\years{2010}\textit{Rella I Cohn fund} Graduate student research funding -- \textsc{asl} fingerspelling data collection

\-\years{2008--}\textit{Graduate Aid Initiative} University of Chicago

\-\years{2007}\textit{University Scholars Program} University of Florida

\pdfbookmark[0]{Experience}{Experience}
\section*{Experience}
\-\years{2011--}\textit{Lab Manager}  \href{http://signlanguagelab.uchicago.edu}{Sign Language Linguistics Laboratory} \hfill University of Chicago \\ Diane Brentari \\

\-\years{2009--}\textit{Research Assistant} \href{http://clml.uchicago.edu/}{Chicago Language Modeling Laboratory} \hfill University of Chicago \\Jason Riggle \\
Automated sign language recognition working group


\-\years{2006}\textit{Research Assistant} Variation in Control Structures \hfill University of Florida\\
Eric Potsdam 

\pdfbookmark[0]{Teaching}{Teaching}
\section*{Teaching}
\-\years{2012}\textit{Lecturer} Introduction to Linguistics \\

\-\years{2012}\textit{Teaching Assistant} Introduction to Linguistics -- Ryan Bochnak\\
\textit{Guest lecture} Sign Language Linguistics

\-\years{2012}\textit{Teaching Assistant} Introduction to Phonetics and Phonology -- Alan Yu\\

\-\years{2011}\textit{Guest lecture} Sign Language Linguistics -- The phonetics of fingerspelling and its relation to \textsc{asl}

\-\years{2011}\textit{Teaching Assistant} Introduction to Syntax -- Amy Dahlstrom\\
\textit{Guest lecture} Crosslinguistic syntactic reflexes of topic and focus


\pdfbookmark[0]{Service}{Service}
\section*{Service}
\-\years{2012}\textit{Reviewer} 48th Annual Meeting of the Chicago Linguistic Society

\-\years{2011}\textit{Graduate Coordinator} for prospective student recruitment activities

\-\years{2011}\textit{Reviewer} 47th Annual Meeting of the Chicago Linguistic Society

\-\years{2011}\textit{Graduate student liaison} to faculty

\-\years{2009--10}\textit{Officer} and \textit{conference organizer} Chicago Linguistic Society

\-\years{2010}\textit{Reviewer} 46th Annual Meeting of the Chicago Linguistic Society

\-\years{2009}\textit{Reviewer} 45th Annual Meeting of the Chicago Linguistic Society (Committee: Syntax)

\pdfbookmark[1]{Memberships}{Memberships}
\subsection*{Memberships}
\label{sec:memberships}
\-\years{2008--}Linguistic Society of America


\pdfbookmark[0]{Publications + talks}{Publications + talks}
\section*{Papers + talks}
\setlength\parskip{1ex}

\vspace{2ex}
\pdfbookmark[1]{Proceedings}{Proceedings}
\subsection*{Proceedings}
\begin{hangparas}{1em}{1}
\-\years{{in press}}\textbf{Jonathan Keane}, Diane Brentari, Jason Riggle. Coarticulation in {\textsc{asl}} fingerspelling. In \textit{Proceedings of the North East Linguistic Society}, vol. 42.
        
        
\-\years{{in press}}\textbf{Jonathan Keane}, Diane Brentari, Jason Riggle. Categorical vs. Gradient: What {\textsc{asl}} fingerspelling teaches us about the phonetics-phonology interface. In \textit{Proceedings of the Texas Linguistics Society}, vol. 13.

\end{hangparas}
         
\vspace{2ex}
\pdfbookmark[1]{Book chapters}{Book chapters}
\subsection*{Book chapters}
\begin{hangparas}{1em}{1}
\-\years{{in press}}\textbf{Jonathan Keane}, Diane Brentari, Jason Riggle. Segmentation and pinky extension in {\textsc{asl}} fingerspelling. In Eric Raimy, Chuck Cairns eds., \textit{The Segment in Phonology and Phonetics}.

\end{hangparas}
         
\vspace{2ex}
\pdfbookmark[1]{Conference presentations}{Conference presentations}
\subsection*{Conference presentations}
\begin{hangparas}{1em}{1}
\-\years{2012}\textbf{Jonathan Keane}, Diane Brentari, Jason Riggle. ``Handshape assimilation in {\textsc{asl}} fingerspelling'' Societas Linguistica Europaea, Loanwords as Evidence in Formal Linguistics
        
        
\-\years{2012}\textbf{Jonathan Keane}, Diane Brentari, Jason Riggle. ``Categorical vs. Gradient: What {\textsc{asl}} fingerspelling teaches us about the phonetics-phonology interface'' Texas Linguistics Society 13
        
        
\-\years{2012}\textbf{Jonathan Keane}, Diane Brentari, Jason Riggle. ``Segments in {\textsc{asl}} fingerspelling'' {\textsc{cuny}} Phonology Forum Conference on the Segment
        
        
\-\years{2012}\textbf{Jonathan Keane}, Diane Brentari, Jason Riggle. ``Handshape and coarticulation in {\textsc{asl}} fingerspelling'' Linguistic Society of America 2012 Annual Meeting
                                     
\-\years{2011}\textbf{Jonathan Keane}, Susan Rizzo, Diane Brentari, Jason Riggle. ``Phonetic coding of fingerspelling'' Building sign language corpora in North America
        
        
\-\years{2011}\textbf{Jonathan Keane}, Erin Dahlgren, Jason Riggle. ``Variation in segment duration in {\textsc{asl}} fingerspelling'' Linguistic Society of America 2011 Annual Meeting

\end{hangparas}
         
\vspace{2ex}
\pdfbookmark[1]{Invited talks}{Invited talks}
\subsection*{Invited talks}
\begin{hangparas}{1em}{1}
\-\years{2011}\textbf{Jonathan Keane}. ``Data coding of, and transition time in, {\textsc{asl}} fingerspelling'' The Language, Cognition, and Computation workshop, University of Chicago

\end{hangparas}
         
\vspace{2ex}
\pdfbookmark[1]{Posters}{Posters}
\subsection*{Posters}
\begin{hangparas}{1em}{1}
\-\years{2012}\textbf{Jonathan Keane}, Diane Brentari, Jason Riggle. ``Pinky extension coarticulation in {\textsc{asl}} fingerspelling'' Illinois Speech Day
                                     
\-\years{2011}\textbf{Jonathan Keane}, Diane Brentari, Jason Riggle. ``Co-articulation in {\textsc{asl}} fingerspelling'' North East Linguistic Society 42: University of Toronto

\end{hangparas}
         
\vspace{2ex}
\pdfbookmark[1]{Qualifying papers}{Qualifying papers}
\subsection*{Qualifying papers}
\begin{hangparas}{1em}{1}
\-\years{2011}\textbf{Jonathan Keane}. \textit{A new look at scrambling in Japanese} University of Chicago defended 24 May 2011 Advisors: Karlos Arregi and Ming Xiang
                                     
\-\years{2010}\textbf{Jonathan Keane}. \textit{Segment duration and the phonetics of fingerspelling {\textsc{asl}}} University of Chicago defended 18 October 2010 Advisors: Jason Riggle and Diane Brentari

\end{hangparas}
         

%
% \subsection*{Software}
% \begin{hangparas}{1em}{1}
%
% \end{hangparas}

\pdfbookmark[0]{Languages}{Languages}
\section*{Languages}
\label{sec:languages}
English~(native), American Sign Language~(intermediate), German~(reading), Japanese~(basic), Hebrew~(basic)

\pdfbookmark[0]{Computer languages + applications}{Computer languages + applications}
\section*{Computer languages + applications}
\label{sec:computer}
Python, {\sc sql}, R, \LaTeX, {\sc (x)html}, \textsc{php}, \textsc{elan}, emacs, OpenOffice, Adobe Photoshop, Adobe Illustrator, Adobe InDesign, Mac OS X, Linux/\textsc{unix}

%\vspace{1cm}
\vfill{}
\hrulefill
\begin{center}
{\footnotesize \href{http://cv.jonkeane.com}{cv.jonkeane.com} — Last updated: \isodate\today}
\end{center}

\end{document}



%%%%%%% TEMPLATE FROM:
%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
%------------------------------------



